### 2017-07-13 doc/manual/version3/inputParameters.tex
Switched from readVMEC to mini_libstell

>>>>

\param{VMEC\_Nyquist\_option}
{integer}
{1}
{Only when \parlink{geometryScheme} == 5.}
{In VMEC, some quantities are known at poloidal and toroidal mode numbers given by the arrays {\ttfamily xm} and
{\ttfamily xn}, whereas other quantities are known at a larger range of mode numbers {\ttfamily xm\_nyq} and {\ttfamily xn\_nyq}.
The sfincs parameter {\ttfamily VMEC\_Nyquist\_option}
controls whether or not to include mode numbers that exist in the {\ttfamily xm\_nyq} and {\ttfamily xn\_nyq}
arrays but not in the {\ttfamily xm} and {\ttfamily xn} arrays.
This this parameter only affects high-frequency components of the magnetic field, results of sfincs
should not be very sensitive to this parameter.
\\

{\ttfamily VMEC\_Nyquist\_option}=1: Only include poloidal and toroidal mode numbers that exist
in the {\ttfamily xm} and {\ttfamily xn} arrays.  This option was always used prior to July 2017.\\

{\ttfamily VMEC\_Nyquist\_option}=2: Also include the larger poloidal and toroidal mode numbers that exist
in the {\ttfamily xm\_nyq} and {\ttfamily xn\_nyq} arrays, where available.
}
